Manuscript_Outputs

### 2024-01-24 Scripts/Data_Management/Scripts_Processing/Prep_TyrerCuzick_input.Rmd
R1.7 no FaH BC father

  v8 <- data %>% transmute(
    t1_FatherBrCa = dplyr::case_when(
      TC_FatherBrCa=="Yes" ~ 1,
      TC_FatherBrCa=="No" ~ 0,
      ), # All No but include anyway for completion
    t2_BrotherBrCa = dplyr::case_when(
      TC_SiblingBrCa == "Yes" & 
        (TC_NSisters == 0 | is.na(TC_NSisters)) & 
        (TC_NBrothers > 0 & !is.na(TC_NBrothers)) ~ 1,
      TRUE ~ 0
    ), # If siblings with breast cancer, no sisters, and brothers then yes, otherwise no
    t3_DensityMeasure = 0,
    t4_DensityValue = -99,
    t5_PRS = 0 #round(TEU_BrCa_313_PRS_center,8)
  )

>>>>

  v8 <- data %>% transmute(
    t1_FatherBrCa = 0, # No data
    t2_BrotherBrCa = dplyr::case_when(
      TC_SiblingBrCa == "Yes" & 
        (TC_NSisters == 0 | is.na(TC_NSisters)) & 
        (TC_NBrothers > 0 & !is.na(TC_NBrothers)) ~ 1,
      TRUE ~ 0
    ), # If siblings with breast cancer, no sisters, and brothers then yes, otherwise no
    t3_DensityMeasure = 0,
    t4_DensityValue = -99,
    t5_PRS = 0 #round(TEU_BrCa_313_PRS_center,8)
  )

### 2024-01-24 Scripts/Stats_Analysis/RMarkdown/ManuscriptOutputs.Rmd
R1.7 no FaH BC father

# Descrp stats
part1 <- tableby(PRS_bc_std_q ~ 
                   # Standard
                   TEU_BaC_AgeCat + Height + Weight +
                   # Reproductive
                   FSF_AgeMenarche + TC_Parity + FSF_AgeMenopause +
                   TC_HRT_imputed +
                   # Diagnoses
                   TC_OvarianCaDx + Biopsy_Prevalent +
                   # Family history
                   TC_MotherBrCa + 
                   TC_NSisters + TC_SiblingBrCa + TC_FatherBrCa,
                 data=data %>% mutate(Biopsy_Prevalent=factor(Biopsy_Prevalent)), 
                 control=my_controls)

@@

tc_varlist <- c("FSF_AgeMenopause", "FSF_AgeMenarche", "Height", "BMI", 
                "AgeFirstBirth", "TC_HRT_imputed", "AtypicalHyperplasia")
                # "TEU_BaC_AgeAtRec", "TC_Parity", 
                # "AtypicalHyperplasia", "TC_OvarianCaDx", "TC_OvarianCaAge", "FSF_HRTDuration", 
                # "FSF_HRT_timesince", "TC_MotherBrCa", "TC_NSisters", "TC_SiblingBrCa", "TC_FatherBrCa")

>>>>

# Descrp stats
part1 <- tableby(PRS_bc_std_q ~ 
                   # Standard
                   TEU_BaC_AgeCat + Height + Weight +
                   # Reproductive
                   FSF_AgeMenarche + TC_Parity + FSF_AgeMenopause +
                   TC_HRT_imputed +
                   # Diagnoses
                   TC_OvarianCaDx + Biopsy_Prevalent +
                   # Family history
                   TC_MotherBrCa + 
                   TC_NSisters + TC_SiblingBrCa,
                 data=data %>% mutate(Biopsy_Prevalent=factor(Biopsy_Prevalent)), 
                 control=my_controls)

@@

tc_varlist <- c("FSF_AgeMenopause", "FSF_AgeMenarche", "Height", "BMI", 
                "AgeFirstBirth", "TC_HRT_imputed", "AtypicalHyperplasia")
                # "TEU_BaC_AgeAtRec", "TC_Parity", 
                # "AtypicalHyperplasia", "TC_OvarianCaDx", "TC_OvarianCaAge", "FSF_HRTDuration", 
                # "FSF_HRT_timesince", "TC_MotherBrCa", "TC_NSisters", "TC_SiblingBrCa")
